### 2018-05-15 submission/manuscript.Rmd
complete removal of sub-sampling and jargon cycle stuff from results

***Prevalence of Chimeric Sequences are HiFi DNA Polymerase Dependent and Correlate with the Number of OTUs:***
There were significant differences in the chimera prevalence based on HiFi DNA polymerase used at all levels of sub-sampling and cycle numbers (P-value `r ifelse(max(filter(kruskal_chimera_prev, sub_sample_level > 500)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S9]. Differences in chimera prevalence between Platinum and all other HiFi DNA polymerases accounted for the majority of these differences [Table S10]. Accuprime^TM^ had the lowest chimera prevalence of all HiFi DNA polymerases regardless of whether 'pre.cluster' or chimera removal with VSEARCH was used [Figure 5]. A positive correlation was observed between chimeric sequences and the number of OTUs for all HiFi DNA polymerases [Figure 6]. This positive correlation was strongest for Accuprime^TM^, Platinum, and Phusion HiFi DNA Polymerases [Figure 6]. The R^2^ value between the number of OTUs and chimeric sequences did not change with the use of 'pre.cluster' or with the removal of chimeras using VSEARCH [Figure 6]. This data suggests that chimera prevalence depends on HiFi DNA polymerase used and confirms that the number of OTUs is dependent on the prevalence of these chimeric sequences.

>>>>

***Prevalence of Chimeric Sequences are HiFi DNA Polymerase Dependent and Correlate with the Number of OTUs:***
There were significant differences in the chimera prevalence based on HiFi DNA polymerase used at all numbers of cycles used (P-value `r ifelse(max(filter(kruskal_chimera_prev)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S9]. Differences in chimera prevalence between Platinum and all other HiFi DNA polymerases accounted for the majority of these differences [Table S10]. Accuprime^TM^ had the lowest chimera prevalence of all HiFi DNA polymerases regardless of whether chimera removal with VSEARCH was used [Figure 5A & 5B]. There was a plateau in the total percent of chimeras that were removed that was similar for all HiFi DNA polymerases [Figure 5C]. A positive correlation was observed between chimeric sequences and the number of OTUs for all HiFi DNA polymerases [Figure 6]. This positive correlation was strongest for Accuprime^TM^, Platinum, and Phusion HiFi DNA Polymerases [Figure 6]. This data suggests that chimera prevalence depends on HiFi DNA polymerase used and confirms that the number of OTUs is dependent on the prevalence of these chimeric sequences.

### 2018-05-15 submission/manuscript.tex
complete removal of sub-sampling and jargon cycle stuff from results

\textbf{\emph{Prevalence of Chimeric Sequences are HiFi DNA Polymerase
Dependent and Correlate with the Number of OTUs:}} There were
significant differences in the chimera prevalence based on HiFi DNA
polymerase used at all levels of sub-sampling and cycle numbers (P-value
\textless{} 0.05) {[}Table S9{]}. Differences in chimera prevalence
between Platinum and all other HiFi DNA polymerases accounted for the
majority of these differences {[}Table S10{]}.
Accuprime\textsuperscript{TM} had the lowest chimera prevalence of all
HiFi DNA polymerases regardless of whether `pre.cluster' or chimera
removal with VSEARCH was used {[}Figure 5{]}. A positive correlation was
observed between chimeric sequences and the number of OTUs for all HiFi
DNA polymerases {[}Figure 6{]}. This positive correlation was strongest
for Accuprime\textsuperscript{TM}, Platinum, and Phusion HiFi DNA
Polymerases {[}Figure 6{]}. The R\textsuperscript{2} value between the
number of OTUs and chimeric sequences did not change with the use of
`pre.cluster' or with the removal of chimeras using VSEARCH {[}Figure
6{]}. This data suggests that chimera prevalence depends on HiFi DNA
polymerase used and confirms that the number of OTUs is dependent on the
prevalence of these chimeric sequences.

>>>>

\textbf{\emph{Prevalence of Chimeric Sequences are HiFi DNA Polymerase
Dependent and Correlate with the Number of OTUs:}} There were
significant differences in the chimera prevalence based on HiFi DNA
polymerase used at all numbers of cycles used (P-value \textless{} 0.05)
{[}Table S9{]}. Differences in chimera prevalence between Platinum and
all other HiFi DNA polymerases accounted for the majority of these
differences {[}Table S10{]}. Accuprime\textsuperscript{TM} had the
lowest chimera prevalence of all HiFi DNA polymerases regardless of
whether chimera removal with VSEARCH was used {[}Figure 5A \& 5B{]}.
There was a plateau in the total percent of chimeras that were removed
that was similar for all HiFi DNA polymerases {[}Figure 5C{]}. A
positive correlation was observed between chimeric sequences and the
number of OTUs for all HiFi DNA polymerases {[}Figure 6{]}. This
positive correlation was strongest for Accuprime\textsuperscript{TM},
Platinum, and Phusion HiFi DNA Polymerases {[}Figure 6{]}. This data
suggests that chimera prevalence depends on HiFi DNA polymerase used and
confirms that the number of OTUs is dependent on the prevalence of these
chimeric sequences.

### 2018-05-15 submission/supplemental.Rmd
complete removal of sub-sampling and jargon cycle stuff from results

mock_chimera_kruskal <- as.data.frame(
  read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  filter(sub_sample_level > 500)

colnames(mock_chimera_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle", "Sub-Sample Depth")

@@

mock_chimera_dunn <- as.data.frame(read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(sub_sample_level > 500, pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh)

colnames(mock_chimera_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle", "Sub-Sample Depth")

>>>>

mock_chimera_kruskal <- as.data.frame(
  read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-sub_sample_level)

colnames(mock_chimera_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle")

@@

mock_chimera_dunn <- as.data.frame(read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")) %>% 
  mutate_at(vars(chi2:Z), funs(round(., digits = 2))) %>% 
  filter(pvalue < 0.05) %>% 
  arrange(pvalue) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  select(-bh, -sub_sample_level) %>% 
  arrange(cycle)

colnames(mock_chimera_dunn) <- c("Chi Squared", "Z Statistic", "P Adjusted", "Comparison", "Cycle")
